Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-10-31 manuscript.tex
updated change macro
Added discussion of exhaustive/scalar asymmetry to .tex file

\usepackage{color}
\definecolor{Blue}{RGB}{0,0,250}
\newcommand{\change}[1]{\textcolor{Blue}{[#1]}}

@@

One outstanding empirical problem is the pattern of response we observed
for \enquote{cat and dog} on trials where there was only a cat on the
card. Because this utterance is strictly false in this world state, it
is surprising -- on both the traditional view as well as on the account
developed here -- that participants assigned this utterance ratings
above \enquote{wrong} with any systematicity. However, this is exactly
what we observed, particulary in the quaternary and quinary conditions
of the experiment, where a sizeable minority of participants considered
this utterance \enquote{kinda right}. As Figure \ref{fig:speakerprobs}
demonstrates, the conditional speaker probability of this utterance in
this world state is 0; thus, there is no conceivable threshold value
that would allow this utterance to ever be rated above \enquote{wrong}
(on the reasonable assumption that the thresholds in our responder model
\(R\) should be nonzero). Any linking hypothesis will have to engage
with this data point, and we leave to future work an analysis which
captures participants' behavior in this condition.

>>>>

\usepackage{color}
\definecolor{Blue}{RGB}{0,0,250}
\newcommand{\change}[1]{\textcolor{Blue}{#1}}

@@

\change{However, the model in its present form already captures an interesting asymmetry in inferred implicature rates between exhaustive and scalar trials of the experiment: note specifically (c.f. Figure 8) that inferred implicature rates are greater in the binary and ternary conditions for scalar trials over exhaustive trials. This is expected given the model’s inferred speaker probabilities: the speaker probability of producing “There is a cat on the card” in the context of there being a cat and dog on the card (an exhaustive implicature-inducing trial) is greater than the speaker probability of producing “There is a cat or a dog on the card” in that same context (a scalar implicature-inducing trial). Recall that these probabilities were derived via the simplifying assumption of uniform cost on utterances; in fact, adding cost to relatively complex disjunctive sentences over simple declarative sentences only predicts a more pronounced asymmetry in the experimentally-observed direction.}

\change{Less readily explained is why this asymmetry disappears with the introduction of more response options, i.e. in the quaternary and quinary conditions. If anything, the opposite numerical trend is observed in these conditions: that is, inferred implicature rates are slightly greater in exhaustive trials over scalar trials. Future work should investigate the interaction between trial type (exhaustive vs. scalar) and number of response options.}

One \change{additional} empirical problem is the pattern of response we observed
for \enquote{cat and dog} on trials where there was only a cat on the
card. Because this utterance is strictly false in this world state, it
is surprising -- on both the traditional view as well as on the account
developed here -- that participants assigned this utterance ratings
above \enquote{wrong} with any systematicity. However, this is exactly
what we observed, particulary in the quaternary and quinary conditions
of the experiment, where a sizeable minority of participants considered
this utterance \enquote{kinda right}. As Figure \ref{fig:speakerprobs}
demonstrates, the conditional speaker probability of this utterance in
this world state is 0; thus, there is no conceivable threshold value
that would allow this utterance to ever be rated above \enquote{wrong}
(on the reasonable assumption that the thresholds in our responder model
\(R\) should be nonzero). Any linking hypothesis will have to engage
with this data point, and we leave to future work an analysis which
captures participants' behavior in this condition.
